Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-24 latex/ms.tex
write 2.1 and start 2.2, #6

\section{Theory}\label{sec2}
In this section, we present the theoretical foundation for estimating a migrant number and a migration rate using HS or PO pairs, which are found between two populations with a different sample timing. While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes. It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers in the two populations; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS or PO pairs. The main symbols used in the current paper are summarized in Table \ref{symbols}.

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate. In this framework, two reproductive seasons (hereafter, we call them "the first year" and "the second year") are enough to estimate it.

Suppose there are $N_1$ parents in the population 1 at the beginning of the first year. Each parent produces offspring in which the number is determined by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$). After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$). Similar to the population, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).

@@

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{{\bf FIGURE 1} \figcapa{}}
		\label{example}
	\end{center}
\end{figure}
%%%%%%%%%%%

>>>>

\section{Theory}\label{sec2}
In this section, we present the theoretical foundation for estimating a migrant number and a migration rate using HS or PO pairs, which are found between two populations with a different sample timing. While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes. It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers for each population; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS and/or PO pairs. The main symbols used in the current paper are summarized in Table \ref{symbols}.

%%%%%%%%%%%%%%
\begin{center}
Table \ref{symbols} is here. 
\end{center}
%%%%%%%%%%%%%%

@@

Suppose that we have a set of two populations labelled 1 and 2 where random mating occurs within each population and that parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the movement of parents in the direction from population 1 to population 2 and focus on the migration number or rate, and that is what we attempt to estimate. In this framework, considering two reproductive seasons (hereafter, we call them "the first year" and "the second year") is enough to estimate it.

Suppose there are $N_1$ parents in the population 1 at the beginning of the first year. Each parent produces offspring in which the number is determined by the parent's reproductive potential, denoted by $\lambda_{i,1}$ ($i=1,2,\ldots,N_1$). After the reproductive season, part of the parents would start to moving towards the population 2; $M$ survived migrants arrive in the population 2 so that there are $N_2$ parents in the population 2 at the beginning of the second year ($M<N_2$). Similar to the population 1, $N_2$ parents produce offspring in which the number is determined by $\lambda_{j,2}$ ($j=1,2,\ldots,N_2$).

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. Additionally, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are also randomly sampled. It should be noted that the four kinds of a sample are not always required for estimating migration number or rate; what kinds of samples are needed depends on the situation, as explained later.

 The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively). As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed. In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.

\textcolor{red}{kokomade!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}

Although the theoretical framework allows a flexible setting of the reproductive potential,

@@

%%%%%%%%%%%%%%
\begin{center}
Figure \ref{cartoon} is here. 
\end{center}
%%%%%%%%%%%%%%

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{{\bf FIGURE 1} \figcapa{}}
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%
